Dominance Regions for Rank Two Cluster Algebras

### 2022-05-30 dominance_regions.tex
Adjustment to proof of Lemma 4.1

  Here we explicitly compute the dominance regions $\cP_\lambda$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    \label{le:cluster monomials}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP_\lambda=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_k^{\alpha_k}x_{k+1}^{\alpha_{k+1}}$.
    In this case, the intersection
    \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
    is precisely $\{\lambda\}$. 
    Indeed, for $k$ odd, the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
    Next, again for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\phi_{k+1}\lambda$.
    In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at $(0,0)$ and $\lambda$.
    Combining these observations proves the result for $k$ odd, the case of even $k$ is similar.
  \end{proof}
  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
  \begin{itemize}
    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth pairs of inequalities become equations for lines which intersect at $\lambda$.
  \end{itemize}
  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.

>>>>

  Here we explicitly compute the dominance regions $\cP_\lambda$.
  When $\lambda$ is not imaginary, the dominance region is particularly simple.
  \begin{lemma}
    \label{le:cluster monomials}
    If $\lambda\in\ZZ^2\setminus\cI$, then $\cP_\lambda=\{\lambda\}$.
  \end{lemma}
  \begin{proof}
    Any such $\lambda$ is the $\bfg$-vector of a cluster monomial, say $x_{k+1}^{\alpha_{k+1}}x_{k+2}^{\alpha_{k+2}}$.
    In this case, the intersection
    \[\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda) \cap \phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)\]
    is precisely $\{\lambda\}$. 
    Indeed, for $k$ odd, the cone $\cC_{k-1}(\phi_{k-1}\lambda)$ lies entirely within a domain of linearity for $\phi_{k-1}^{-1}$.
    In particular, $\phi_{k-1}^{-1}\cC_{k-1}(\phi_{k-1}\lambda)$ is a cone containing $\lambda$ directed away from the origin (with walls parallel to the boundary of the domain of linearity containing $\lambda$).
    Next, again for $k$ odd, the cone $\cC_{k+1}(\phi_{k+1}\lambda)$ intersects the domain of linearity for $\phi_{k+1}^{-1}$ containing $\phi_{k+1}\lambda$ in a (possibly degenerate) convex quadrilateral with corners at the origin and $\phi_{k+1}\lambda$.
    In particular, the intersection of $\phi_{k+1}^{-1}\cC_{k+1}(\phi_{k+1}\lambda)$ with the cone containing $\lambda$ is a (possibly degenerate) convex quadrilateral with corners at the origin and $\lambda$.
    Combining these observations proves the result for $k$ odd, the case of even $k$ is similar.
  \end{proof}
  To compare with Theorem~\ref{th:dominance inequalities}, we consider three cases in which $\lambda\in\ZZ^2\setminus\cI$:
  \begin{itemize}
    \item if $\lambda_0 \le 0$ and $\lambda_1 \ge 0$, the second and fourth pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_0 > 0$ and $\lambda_1 \ge \frac{-bc+\sqrt{bc(bc-4)}}{2b}\lambda_0$, the first and second pairs of inequalities become equations for lines which intersect at $\lambda$;
    \item if $\lambda_1 < 0$ and $\lambda_0 \le \frac{bc-\sqrt{bc(bc-4)}}{2c}\lambda_1$, the third and fourth pairs of inequalities become equations for lines which intersect at $\lambda$.
  \end{itemize}
  This proves Theorem~\ref{th:dominance inequalities} when $\lambda\notin\cI$.
